Pillar 1 - Sequential Pattern Mining

### 2019-03-14 Pillar 1 - Sequential Pattern Mining.Rmd

## Transactions
```{r making transactions, cache = TRUE}
make_transaction <- function(data, item){

@@

}

transactions <- tribble(
  ~ ID   ,  ~ data                    , ~ item,
  "taken", d_transactions$taken_PF_HL, quo(item),
  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
  "TPF"  , d_transactions$T_PF_HL    , quo(item_TPF),
  "THL"  , d_transactions$T_PF_HL    , quo(item_TPF),
  "G"    , d_transactions$G          , quo(item_g)
  ) %>%

  mutate(transactions = list(data, item) %>% pmap(make_transaction))

inspect(head(transactions$transactions[[2]], 10))
```

## Sequences
```{r making sequences, cache = TRUE}
make_sequence <- function(data, item){

@@

}

sequences <- tribble(
  ~ ID   ,  ~ data                    , ~ item,
  "taken", d_transactions$taken_PF_HL, quo(item),
  "PF"   , d_transactions$taken_PF_HL, quo(item_PF),
  "HL"   , d_transactions$taken_PF_HL, quo(item_HL),
  "G"    , d_transactions$G          , quo(item_g)
  ) %>%

  mutate(sequences = list(data, item) %>% pmap(make_sequence))

inspect(head(sequences$sequences[[2]], 10))
```

>>>>

## Transactions and sequences
```{r make_transaction}
make_transaction <- function(data, item){

@@

```{r make_sequence}
make_sequence <- function(data, item){

  if(item == sym("item_TPF") | item == sym("item_THL")) return("Compute sequences that include courses nto taken yet by hand")

@@

```{r transactions, cache = TRUE}
transactions <- tribble(
  ~ ID   ,  ~ data                   , ~ item,
  "taken", d_transactions$taken_PF_HL, sym("item"),
  "PF"   , d_transactions$taken_PF_HL, sym("item_PF"),
  "HL"   , d_transactions$taken_PF_HL, sym("item_HL"),
  "TPF"  , d_transactions$T_PF_HL    , sym("item_TPF"),
  "THL"  , d_transactions$T_PF_HL    , sym("item_TPF"),
  "G"    , d_transactions$G          , sym("item_g")
  ) %>%

  mutate(
    transactions = list(data, item) %>% pmap(make_transaction),
    sequences    = list(data, item) %>% pmap(make_sequence   )
    )

inspect(head(transactions$transactions[[3]], 10))
inspect(head(transactions$sequences   [[3]], 10))
```
